### 2016-04-22 doc/publications/plos16/plos16.tex
2 sections -- parameter settings and decision trees

\subsection*{Random forest is sensitive to tree depth}

>>>>

\subsection*{Parameter settings}
\marginpar{ was''Random forest is sensitive to tree depth''}
In this setting, variable selection in very high dimensions, we nned to consider the parameter setting for the RF
algorithm.

I will use the R terms from the package RandomForests whcih incoporates the original Fortran code by Brieman and
Cutler. We consider the parameters:
\begin{itemize}
\item \texttt{max_depth} the size (complexity) of the individual trees
\item \texttt{ntree} the number of trees 
\item \texttt{mtry} --  the number of variables considered at each split (if \texttt{mtry}=$p$, we have a boosted decison
  tree model \marginpar{is this right?}
\end{itemize}

We note that it is possible for a RF model to have a very poor fit, and be useless for prediction, and still have a 
useful ranking of variable importance.

\subsection*{decision trees }
\begin{itemize}
\item benefits os a decision tree
  \begin{itemize}
  \item invariant to scale of the input data
  \item handles categorical and real valued inputs 
  \item can handle missing values 
  \item insensitive to useless predictors
  \end{itemize}
\item benefits of random forests
  \begin{itemize}
  \item variable importance 
  \item inherits the qualities of tree models
  \end{itemize}
\end{itemize}
